\documentclass{article}
\usepackage[nottoc]{tocbibind}
\usepackage{url}
\begin{document}


\title{Requirements for writing a bachelor thesis}
\author{Adam Saidane}
\date{October 2020}
\maketitle
\tableofcontents
\section{Requirements for the thesis}
The bachelor project must document the student's understanding and ability to reflect over professional practices and application of theory and methods in relation to a practical problem statement. The problem statement should be central to the education and profession, formulated by the student, possibly in collaboration with a private or public company. The school must approve of the problem statement\cite[my translation]{curriculum}. 

\subsection{Learning objectives}
The student must prove that they have gained knowledge, skills and competencies during their education.  
\subsubsection{The knowledge the student has gained must include: } 
\begin{itemize}
	\item The strategic role of tests in system development. 
	\item Globalization of software production. 
	\item System architecture and understanding of it's strategic meaning for the company's business. 
	\item Utilized theory and methods and technologies from the domain. 
	\item Different types of databases and their application. 
\end{itemize} \cite[my translation]{curriculum}

\subsubsection{The skills the student has gained must include: }
\begin{itemize}
	\item Integrate it-systems and develop systems, which support future integration.
	\item Use contracts as a management and coordination tool in the development process. 
	\item Evaluate and choose databases and design, redesign and optimize databases.
	\item Plan and manage development processes with many geographically separated participants.
	\item Plan and complete testing of larger it-systems.
\end{itemize}\cite[my translation]{curriculum}

\subsubsection{The competencies the student has gained must include: }
\begin{itemize}
	\item Identify relation between applied theory, methodology and can reflect over their suitability in different situations. 
	\item Participate in a professional collaboration for development of large systems by applying widespread methods and technologies. 
	\item Familiarize themselves with new technologies and standards for handling integration between systems.
	\item Develop their own competence profile from being primarily a backend-developer to handle tasks as a system architect through practice.
	\item To determine and realize a business as well as a technologically appropriate architecture for large systems.
\end{itemize} \cite[my translation]{curriculum}
\section{Formalities}
The maximum size of the bachelor thesis is 40 normal pages (2400 characters per page) + 20 normal pages per student. There is no minimum requirement for the size of the thesis.\cite{formalities}  That means a student who writes his thesis alone must at max write 60 pages, and a group of two students must at max write 80 pages.

\section{Content}
The bachelor report must focus on one or more of the mandatory courses of the program, which includes: 
\begin{itemize}
	\item System integration
	\item Test
	\item Databases for Developers
	\item Large Systems Development
\end{itemize}\cite{content}

\bibliographystyle{plain}
\bibliography{references.bib}

\end{document}